[dcpo_demsupport]

### 2020-09-29 paper/dcpo_demsupport.Rmd
starting the result

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dpi = 300)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  huxtable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker # visualization
)

@@

```{r country-years, eval=FALSE}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

@@

Our reanalysis follows the following steps. Frist, we replicated Claassen's  (2019,2020)  studies by using his measurement and analysis models.
Results here.
Next, adding measurement uncertainty into Claassen's analysis models, we found xxxx.
Tables and results here.
We then reanalyzed the relationship between public democratic attitude and democracy institution in both directions, using more data, the DCPO measurement model and measurement uncertainty incorporated.
Results here. indistinguishable from zero.

@@

```{r dataInput, eval = FALSE}

```{r claassenUncertaintyAJPS,eval=FALSE}

```{r dcpoPointAJPS, eval=FALSE}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

```{r dcpoUncertaintyAJPS, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

```{r visualizedMoodAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization"}

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty", eval=FALSE}

```{r dcpoPointAPSR, eval = FALSE}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

```{r dcpoUncertaintyAPSR, eval = FALSE}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

```{r visualizedMoodAPSR, fig.cap= "Effects of Democracy on Change in Mood"}

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", eval = FALSE}

@@

>>>>

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE, dpi = 300)

@@

# load all the packages you will use below 
p_load(
  dataverse, # data scraping
  DCPOtools,
  boot, plm, # analysis
  flextable, kableExtra, modelsummary, # tabulation
  gridExtra,
  latex2exp, # visualization
  rstan, # Bayesian estimation
  tidyverse, # data wrangling
  dotwhisker, # visualization
)

@@

```{r country-years}
path_df <-
  list.files(
    "../data",
    pattern = ".*_theta.rda",
    recursive = TRUE,
    full.names = TRUE
  ) %>%
  .[str_which(., "claassen")]

@@

<!-- I may suggest to move this paragraph to the beginning of the previous section or a separate section of research design -->

**To examine the influence of empirical uncertainty, we conducted a three-step test. 
We first reproduced @Claassen2019.
Then applying the method he described in the article, we replicated his IRT-based measurement of democratic mood and maintain the entire distribution of the predicted outcome, instead of aggregating to a single point estimate.
Utilizing the estimated distribution, we involved uncertainty to the analysis of the influence of democratic mood on institutional democracy cross-nationally.
In the third step, we applied an advanced method and added one-third more data to the analysis to reduce potential effects of measurement biases and data spareness.
We compared the outcomes of the three steps and showed as below that uncertainty is an critical factor in the studies of mass democratic attitude, which may alter the analytic conclusions. 
We further show that accounting for uncertainty is at least equivalently important when the latent-variable estimates plays as the dependent variable in a study by replicating Claassen2020b. **

```{r dataInput}

```{r claassenUncertaintyAJPS}

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

```{r dcpoUncertaintyAJPS}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

```{r visualizeAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization", eval = TRUE}

df_tableAJPS <- df_plotS %>% mutate(
  std.error = ifelse(is.na(std.error), se, std.error)
) %>% 
  select(term, estimate, std.error, model)

```{r visualizedUncertainAJPS, fig.cap= "The Effect of Democratic Mood on Institutional Democratization Accounting for Uncertainty"}

```{r dcpoPointAPSR}
df_controls <- read_csv(here::here("data", "control_variables_apsr.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name")) %>% 
  filter(year >= firstyear)

```{r dcpoUncertaintyAPSR}
df_dcpo <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    reformat_dcpo_output("theta") %>% 
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country")) %>%
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

```{r visualizedAPSR, fig.cap= "Effects of Democracy on Change in Mood", eval = TRUE}

```{r visualizedUncertaintyAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO"}

The results are presented in Figure \@ref(fig:visualizeAJPS)

# Discussion

@@

@@

# (APPENDIX) Appendix {-},

## Models of Effect of Democratic Mood on Institutional Democratization

```{r tableAJPS}

## Models of Effects of Democracy on Change in Mood
